Title of Paper

### 2017-02-16 paper.tex
revise vectorization discusson

\subsection{Data Ordering and Vectorization Patterns}
For a chemical kinetic model with species $k$ for the $j$-th thermo-chemical state to be evaluated, $[C_k]_j$ there are two choices for data-storage in memory.
In the ``C'' (row-major) format, species concentrations for $j$-th thermo-chemical state are stored sequentially in memory, i.e.: $[C_0]_0\text{,}\allowbreak C[1]_0\ldots\allowbreak [C_{N_S}]_0\text{,}\allowbreak [C_0]_1\allowbreak\ldots\allowbreak [C_{N_S}]_N$, where $N$ is the total number of thermo-chemical conditions.
Alternatively, in the ``F'' (Fortan column-major) format species concentrations a single species for all thermo-chemical states are sequential, i.e.: $[C_0]_0\text{,}\allowbreak[C_0]_1\ldots\allowbreak[C_0]_N\text{,}\allowbreak[C_1]_0\ldots\allowbreak[C_{N_S}]_N$
In Sec.~\ref{S:results} the effect of this ordering will be shown to have a large performance impact on the program runtime.

In this work, a \textit{shallow}-SIMD vectorization has been implemented, entailing each SIMD-lane evaluating the species rates for an thermo-chemical state independently.
In future efforts, a so called \textit{deep}-SIMD vectorization will be pursued allowing vector-units to cooperate to evaluate species rates for a single thermo-chemical state.
A deep-vectorization may result in SIMD-\textit{waste} in this context---similar to thread-divergence in SIMT-processing---caused by different SIMD-lanes executing different instructions (e.g. from differing for-loop bounds), however past studies demonstrate the merits of deep-SIMT vectorization on GPUs~\cite{Sewerin20151375}.

@@

\begin{table}[ht]
\sisetup{retain-zero-exponent=true}
\centering
\begin{tabular}{@{}S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] @{}}
\toprule
\multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$E_{R_{i}^{\prime}}$} & \multicolumn{1}{c}{$E_{R_{i}^{\prime\prime}}$} &\multicolumn{1}{c}{$E_{R_{i}}$} & \multicolumn{1}{c}{$\text{P}_{\text{min}}^{*}\si{\percent}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[C_k]}{\text{d}t}}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[T]}{\text{d}t}}$} \\
\midrule
\multicolumn{1}{c}{\ce{H2}\slash~\ce{CO}} & 1.20e-8 & 6.33e-8 & 1.32e1 & 4.66e6 & 2.37e1 & 2.12e5 \\
\multicolumn{1}{c}{GRI-Mech.~3.0}  & 3.07e-8 & 5.90e-8 & 1.21e0 & 2.67e04 & 2.84e0 & 2.64e4 \\
\multicolumn{1}{c}{USC-Mech II}  & 1.07e-7 & 1.37e-7 & 2.39e0 & 4.12e02 & 7.92e00 & 3.22e03 \\
\bottomrule
\end{tabular}
\caption{Summary of rate of progress, species and temperature rate correctness.
Error statistics are based on the infinity-norm of the relative error detailed in Eq.~\eqref{e:rel_err} for each quantity.
}
\label{T:error}
\end{table}

>>>>

\subsection{Data Ordering and Vectorization Patterns}
For a chemical kinetic model with species $k$ for the $j$-th thermo-chemical state to be evaluated, $[C_k]_j$ there are two choices for data-storage in memory.
In the ``C'' (C row-major) format, species concentrations for $j$-th thermo-chemical state are stored sequentially in memory.
Alternatively, in the ``F'' (Fortan column-major) format species concentrations a single species for over all thermo-chemical states are adjacent in memory.
In Sec.~\ref{S:results} the effect of this ordering will be shown to have a large performance impact on the program runtime.

In this work, a \textit{shallow}-SIMD vectorization has been implemented, entailing each SIMD-lane evaluating chemical source terms for an thermo-chemical state independently.
In future efforts, a so called \textit{deep}-SIMD vectorization will be pursued allowing vector-units to cooperate to evaluate species rates for a single thermo-chemical state.
A deep-vectorization may result in SIMD-\textit{waste} in this context---similar to thread-divergence in SIMT-processing---caused by different SIMD-lanes executing different instructions (e.g. from differing for-loop bounds).
However a deep-vectorization will likely have higher cache hit-rates than a shallow-vectorization using the ``C'' memory layout as successive SIMD-lanes would access directly memory adjacent locations.
Additionally, past studies demonstrate the merits of deep-SIMT vectorization on GPUs~\cite{Sewerin20151375}.

@@

\begin{table}[ht]
\sisetup{retain-zero-exponent=true}
\centering
\begin{tabular}{@{}S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] S[table-format=1.2e1] @{}}
\toprule
\multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$E_{R_{i}^{\prime}}$} & \multicolumn{1}{c}{$E_{R_{i}^{\prime\prime}}$} &\multicolumn{1}{c}{$E_{R_{i}}$} & \multicolumn{1}{c}{$\text{P}_{\text{min}}^{*}\si{\percent}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[C_k]}{\text{d}t}}$} & \multicolumn{1}{c}{$E_{\frac{\text{d}[T]}{\text{d}t}}$} \\
\midrule
\multicolumn{1}{c}{\ce{H2}\slash~\ce{CO}} & 1.20e-8 & 6.33e-8 & 1.32e1 & 4.66e6 & 2.37e1 & 2.12e5 \\
\multicolumn{1}{c}{GRI-Mech.~3.0}  & 3.07e-8 & 5.90e-8 & 1.21e0 & 2.67e04 & 2.84e0 & 2.64e4 \\
\multicolumn{1}{c}{USC-Mech II}  & 1.07e-7 & 1.37e-7 & 2.39e0 & 4.12e02 & 7.92e00 & 3.22e03 \\
\bottomrule
\end{tabular}
\caption{Summary of rate of progress, species and temperature rate correctness.
Error statistics are based on the infinity-norm of the relative error detailed in Eq.~\eqref{e:rel_err} for each quantity.
\todo[inline]{i-pentanol validation still running}
}
\label{T:error}
\end{table}
